Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
fucking rewrite

We shall explore a simpler caching mechanism that creates a static cache at the start of decoding of the most likely translation rules to be used.

@@

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. The lexicalized reordering model retains its own weights in the log-linear framework. The total weighted score is expected to be identical to the Moses baseline apart from rare training configurations where the lexicalized reordering model is trained on a different dataset than the translation model.

>>>>

We shall explore a simpler caching mechanism by creating a static cache of the most likely translation rules to be used at the start of decoding.

@@

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. The lexicalized reordering model retains its own weights in the log-linear framework. The total weighted score is expected to be identical to the Moses baseline apart from edge case training configurations, for example, where the lexicalized reordering model is trained on a different dataset than the translation model.
